---
title: "EBA_2020_transparency_exercise"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{EBA_2020_transparency_exercise}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(syslosseval)
library(tidyverse)
library(xtable)
```

Generate the stressed data:

```{r}
stress_data_2020 <- make_stress_data(eba_exposures_2020, eba_impairments_2020, 1, 2019)
data_2020 <- make_state_variables(stress_data_2020)

stress_data_2021 <- make_stress_data(eba_exposures_2020, eba_impairments_2020, 2, 2019)
data_2021 <- make_state_variables(stress_data_2021)

stress_data_2022 <- make_stress_data(eba_exposures_2020, eba_impairments_2020, 3, 2019)
data_2022 <- make_state_variables(stress_data_2022)
```

Generate the base dataset:

```{r}
initial_state <- make_table_initial_state(data_2020) %>% 
  add_column(State = "initial_2019") %>%
  add_column(Case = "No_Del") %>% 
  rename(Total_Assets = a_0) %>% 
  rename(CET1 = e_0) %>% 
  rename(Leverage = lambda_0)

stress_state_2020 <- make_table_stress_state(data_2020) %>% 
  add_column(State = "adverse_2020")%>% 
  add_column(Case="No_Del") %>% 
  rename(Total_Assets = a_1) %>% 
  rename(CET1 = e_1) %>% 
  rename(Leverage = lambda_1)

stress_state_2021 <- make_table_stress_state(data_2021) %>% 
  add_column(State = "adverse_2021")%>%
  add_column(Case="No_Del") %>% 
  rename(Total_Assets = a_1) %>% 
  rename(CET1 = e_1) %>% 
  rename(Leverage = lambda_1)

stress_state_2022 <- make_table_stress_state(data_2022) %>% 
  add_column(State = "adverse_2022")%>%
  add_column(Case ="No_Del") %>% 
  rename(Total_Assets = a_1) %>% 
  rename(CET1 = e_1) %>% 
  rename(Leverage = lambda_1)
```

Unlike in 2016 with the 202 dataset we will have banks in the stress scenario the capital of which is completely wiped out in the stress state. We need to isolate these from the data before going into a deeper analysis of the remaining
banks.

```{r}
fundamental_defaulters_2020 <- stress_state_2020 %>% 
  filter(Leverage > 100)
fundamental_defaulters_2021 <- stress_state_2021 %>% 
  filter(Leverage > 100)
fundamental_defaulters_2022 <- stress_state_2022 %>% 
  filter(Leverage > 100)
```

Compute the share of the total assets of the fundamentally insolvent banks in the total assets of all 121 banks in
the system.

Total assets:

```{r}
a <- initial_state %>% summarize(Total = sum(Total_Assets))
b <- fundamental_defaulters_2020 %>% summarize(Total_2020 = sum(Total_Assets))
c <- fundamental_defaulters_2021 %>% summarize(Total_2021 = sum(Total_Assets))
d <- fundamental_defaulters_2022 %>% summarize(Total_2022 = sum(Total_Assets))

share_tabel_total_assets <- bind_cols(a,b,c,d) %>% 
  mutate(share_2020 = Total_2020/Total) %>% 
  mutate(share_2021 = Total_2021/Total) %>% 
  mutate(share_2022 = Total_2022/Total)

share_tabel_total_assets

```

Combine all data in a long dataframe excluding the banks whith CET1=0.

```{r}
leverage_data_no_del <- bind_rows(initial_state, stress_state_2020, stress_state_2021, stress_state_2022) %>%
  mutate(State = factor(State, levels = c("initial_2019", "adverse_2020", "adverse_2021", "adverse_2022")))
```

```{r}
exceeders_no_del <- leverage_data_no_del %>% 
  filter(Leverage >= 33)
```

```{r}
exceed_no_del <- ggplot(data=exceeders_no_del, mapping = aes(x=State, fill = State))

exceed_plot_2020 <- exceed_no_del + geom_bar()+
  scale_x_discrete(labels=c("initial_2019" = "2019", "adverse_2020" = "2020",
                              "adverse_2021" = "2021", "adverse_2022" = "2022"))+
  scale_fill_discrete(name = "State", labels = c("Initial state year end 2019", 
                                                 "Adverse scenario 2020", "Adverse scenario 2021",
                                                 "Adverse scenario 2022"))+
  labs(x="Year")+
  labs(y="Number of Banks")+
  coord_flip()

#exceed_plot_2020
ggsave(filename = "../paper/Figures/exceed_plot_2020.png", plot = exceed_plot_2020)
```

```{r}
aux1 <- initial_state %>% summarize(Total=sum(CET1))
aux2 <- stress_state_2020 %>% summarize(Total_2020 = sum(CET1))
aux3 <- stress_state_2021 %>% summarize(Total_2021 = sum(CET1))
aux4 <- stress_state_2022 %>% summarize(Total_2022 = sum(CET1))

share_table_total_cet1 <- bind_cols(aux1,aux2,aux3,aux4) %>% 
  mutate(cet1_share_2020 = 1-Total_2020/Total) %>% 
  mutate(cet1_share_2021 = 1-Total_2021/Total) %>% 
  mutate(cet1_share_2022 = 1-Total_2022/Total)

share_table_total_cet1
```

# Fire selling

```{r}
fix_2020 <- fixed_point_computation_function(mat = data_2020, lb = 33, data_idx = sovereign_bond_indices,
            data_adv = average_daily_volume_sovereign, base_year = 2019, constant = 1.5)
```

```{r}
fix_2021 <- fixed_point_computation_function(mat = data_2021, lb = 33, data_idx = sovereign_bond_indices,
            data_adv = average_daily_volume_sovereign, base_year = 2019, constant = 1.5)
```

```{r}
fix_2022 <- fixed_point_computation_function(mat = data_2022, lb = 33, data_idx = sovereign_bond_indices,
            data_adv = average_daily_volume_sovereign, base_year = 2019, constant = 1.5)
```

Make a table with the values of the fixed points

```{r}
c1 <- fix_2020 %>% select(sec_class, delta_lower) %>% 
  rename(delta_2020 = delta_lower)
c2 <- fix_2021 %>% select(delta_lower) %>% 
  rename(delta_2021 = delta_lower)
c3 <- fix_2022 %>% select(delta_lower) %>% 
  rename(delta_2022 = delta_lower)

fixed_points <- bind_cols(c1,c2,c3)
```


Write a Latex-table

```{r}
latex_fixed_points <- xtable(fixed_points)
print(latex_fixed_points, file = "../paper/Tables/fixed_points_2020.txt")
```

Compare to the maximum impact:

```{r}
max_delta_2020 <- fix_2020 %>% 
  mutate(rel_2020 = delta_upper/delta_max)

max_delta_2021 <- fix_2021 %>% 
  mutate(rel_2021 = delta_upper/delta_max)

max_delta_2022 <- fix_2022 %>% 
  mutate(rel_2022 = delta_upper/delta_max)
```

Make a table

```{r}
aux1 <- max_delta_2020 %>% 
  select(sec_class, delta_max, rel_2020)
aux2 <- max_delta_2021 %>% 
  select(rel_2021)
aux3 <- max_delta_2022 %>% 
  select(rel_2022)

rel_table <- bind_cols(aux1, aux2, aux3)
```

Make a latex table

```{r}
latex_rel_table <- xtable(rel_table)
print(latex_rel_table, file = "../paper/Tables/rel_table_2020.txt")
```


Table of the computation results


```{r}
stress_state_2020_del <- make_table_final_state(data_2020, fix_2020, 33) %>% 
  add_column(State = "adverse_2020")%>% 
  add_column(Case="Del") %>% 
  rename(Total_Assets = a_1_tau) %>% 
  rename(CET1 = e_1_tau) %>% 
  rename(Leverage = lambda_1_tau)

stress_state_2021_del <- make_table_final_state(data_2021, fix_2021, 33) %>% 
  add_column(State = "adverse_2021")%>%
  add_column(Case="Del") %>% 
  rename(Total_Assets = a_1_tau) %>% 
  rename(CET1 = e_1_tau) %>% 
  rename(Leverage = lambda_1_tau)

stress_state_2022_del <- make_table_final_state(data_2022, fix_2022, 33) %>% 
  add_column(State = "adverse_2022")%>%
  add_column(Case ="Del") %>% 
  rename(Total_Assets = a_1_tau) %>% 
  rename(CET1 = e_1_tau) %>% 
  rename(Leverage = lambda_1_tau)
```

Bind all data into one frame

```{r}
leverage_data_del <- bind_rows(stress_state_2020_del, stress_state_2021_del, stress_state_2022_del) %>% 
  mutate(State = factor(State, levels = c("adverse_2020", "adverse_2021", "adverse_2022")))
```

Exceeders:

```{r}
exceeders_del <- leverage_data_del %>% 
  filter(Leverage >= 33)
```

```{r}
set1 <- filter(exceeders_no_del, State == "adverse_2021")
set2 <- filter(exceeders_del, State == "adverse_2021")
```

# Losses in equity:

```{r}
relative_cet1_del <- leverage_data_del %>% 
  group_by(State) %>% 
  summarize(Tot = sum(CET1))
```

```{r}
total_cet1 <- leverage_data_no_del %>% 
  filter(State == "initial_2019") %>% 
  summarize(Total = sum(CET1))
```

```{r}
comp_data_no_del <- leverage_data_no_del %>%
  select(Bank_name, CET1, State, Case) 

aux <- filter(comp_data_no_del, State == "initial_2019") %>% 
  mutate(Case = "Del")

comp_data_del <- bind_rows(aux, leverage_data_del) %>%  
  select(Bank_name, CET1, State, Case) 
```

We need to transform the data for our computations:

```{r}
comp_data_no_del_trans <- comp_data_no_del %>% 
  pivot_wider(names_from = "State", values_from= "CET1") %>% 
  mutate("Loss 2020" = 1 - adverse_2020/initial_2019) %>% 
  mutate("Loss 2021" = 1 - adverse_2021/initial_2019) %>% 
  mutate("Loss 2022" = 1 - adverse_2022/initial_2019) %>% 
  select(Bank_name, "Loss 2020", "Loss 2021", "Loss 2022", Case) %>% 
  pivot_longer(!c("Bank_name", "Case"), names_to = "Losses", values_to = "Percent")
```

```{r}
comp_data_del_trans <- comp_data_del %>% 
  pivot_wider(names_from = "State", values_from= "CET1") %>% 
  mutate("Loss 2020" = 1 - adverse_2020/initial_2019) %>% 
  mutate("Loss 2021" = 1 - adverse_2021/initial_2019) %>% 
  mutate("Loss 2022" = 1 - adverse_2022/initial_2019) %>% 
  select(Bank_name, "Loss 2020", "Loss 2021", "Loss 2022", Case) %>% 
  pivot_longer(!c("Bank_name", "Case"), names_to = "Losses", values_to = "Percent")
```

```{r}
compare_data_cet1 <- bind_rows(comp_data_no_del_trans, comp_data_del_trans)
```

```{r}
aux_plot <- ggplot(data = compare_data_cet1, mapping = aes(x = Case, y = Percent, fill = Case))

compare_plot <- aux_plot + geom_boxplot(alpha = 0.5) +
  scale_x_discrete(labels=c("Del" = "Del.", "No_Del" = "No Del.")) +
  scale_fill_discrete(name = "Case", labels = c("Deleveraging", "No Deleveraging"))+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  facet_wrap(~Losses)

compare_plot
ggsave(filename = "../paper/Figures/cet1_losses.png", plot = compare_plot)
```
