---
title: "Systemic Loss Evaluation for Banking Systems"
author: Martin Summer
date: 15.3.2021
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Systemic_Loss_Evaluation_for_Banking_Systems}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette provides a brief introduction to the \code{syslosseval} package, a collection of
functions and data to perform the analysis in the paper *Systemic Loss Evaluation* by Thomas
Breuer, Martin Summer and Branko Urosevic.

# Installing the package from Github

To use the package, you first have to install it from GitHub. Here are the necessary steps:

## Step 1: Install the devtools package:

To install a R package, start by installing the devtools package. The best way to do this is from CRAN, by typing:

```{r install-dev-tools}
install.packages("devtools")
```

## Step 2: Install the syslosseval package from GitHub

Install the package of interest from GitHub using the following code, where 
you need to remember to list both the author and the name of the package 
(in GitHub jargon, the package is the repo, which is short for repository). 
In this example, we are installing the syslosseval package created by Martin-Summer-1090.

```{r install-syslosseval}
library(devtools)
install_github("Martin-Summer-1090/syslosseval")
```

## Step 3: Load the package

```{r setup}
library(syslosseval)
```

# Using the package
